Machine Learning Methods for Site-specific Input Management

### 2022-02-07 Codes/PrepareResults.rmd

```{r}
theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain", family = "Cambria"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain", family = "Cambria"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain", family = "Cambria"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain", family = "Cambria"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)

>>>>

```{r}

theme_update(
  axis.title.x =
    element_text(
      size = 12, angle = 0, hjust = .5, vjust = -0.3, face = "plain", family = "Cambria"
    ),
  axis.title.y =
    element_text(
      size = 12, angle = 90, hjust = .5, vjust = .9, face = "plain", family = "Cambria"
    ),
  axis.text.x =
    element_text(
      size = 10, angle = 0, hjust = .5, vjust = 1.5, face = "plain", family = "Cambria"
    ),
  axis.text.y =
    element_text(
      size = 10, angle = 0, hjust = 1, vjust = 0, face = "plain", family = "Cambria"
    ),
  axis.ticks =
    element_line(
      size = 0.3, linetype = "solid"
    ),
  axis.ticks.length = unit(.15, "cm"),
  #--- legend ---#
  legend.text =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
    ),
  legend.title =
    element_text(
      size = 10, angle = 0, hjust = 0, vjust = 0, face = "plain", family = "Cambria"
    ),
  legend.key.size = unit(0.5, "cm"),
  #--- strip (for faceting) ---#
  strip.text = element_text(size = 10),
  #--- plot title ---#
  plot.title = element_text(family = "Times", face = "bold", size = 12),
  #--- margin ---#
  # plot.margin = margin(0, 0, 0, 0, "cm"),
  #--- panel ---#
  panel.grid.major = element_blank(),
  panel.grid.minor = element_blank(),
  panel.background = element_blank(),
  panel.border = element_rect(fill = NA)
)
